The \dealii{} Library, Version 8.5

### 2017-03-09 8.5/paper.tex
Reformat and improve introduction

\item The \texttt{LinearOperator} class has been extended to fully support {\trilinos} solvers.

\item A dedicated physics module has been created to provide some standard definitions and operations used in continuum physics.

\item \texttt{FE\_Enriched}

\item \texttt{FESeries} namespace, use in step-27

@@

\item More than 230 other features and bugfixes.\\
  We realized that static code analyzers are valuable tools to improve and maintain the quality of the code in our library 
  on top off build and regression tests for a variety of setups using \href{https://cdash.kyomu.43-1.org/index.php?project=deal.II}{CDash}.
  This release was tested with \href{http://cppcheck.sourceforge.net/}{Cppcheck}, 
  \href{https://www.viva64.com/en/pvs-studio/}{PVS-Studio} and \href{https://scan.coverity.com/}{Coverity-Scan}. 
  For the latter the current status can be observed \href{https://scan.coverity.com/projects/deal-ii}{online}.
\end{itemize}
The more important ones of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

>>>>

\item The \texttt{LinearOperator} class has been extended by a generic
  ``payload'' mechanism that allows to attach arbitrary additional
  information to a \texttt{LinearOperator}. The mechanism was used to
  implement a \texttt{TrilinosPayload} class to have full support for using
  the suite of {\trilinos} iterative solvers and preconditioners with a
  \texttt{LinearOperator}.

\item A dedicated physics module has been created to provide some standard
  definitions and operations used in continuum mechanics.

\item TODO \texttt{FE\_Enriched}

\item TODO \texttt{FESeries} namespace, use in step-27

@@

\item We realized that static code analyzers are valuable tools to improve
  and maintain the quality of the code in our library on top off build and
  regression tests for a variety of setups using
  \href{https://cdash.kyomu.43-1.org/index.php?project=deal.II}{CDash}.
  This release was tested with
  \href{http://cppcheck.sourceforge.net/}{Cppcheck},
  \href{https://www.viva64.com/en/pvs-studio/}{PVS-Studio} and
  \href{https://scan.coverity.com/}{Coverity-Scan}. For the latter the
  current status can be observed
  \href{https://scan.coverity.com/projects/deal-ii}{online}.

  \item More than 230 other features and bugfixes.
\end{itemize}
The more important ones of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.
